\pkg{partykit}: A Modular Toolkit for Recursive Partytioning in \proglang{R}

### 2015-01-06 pkg/partykit/inst/mloss/letter_mloss4.tex
add letter
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@678 255f4249-2263-4417-b1ea-8498779e27a7

\subject{JMLR-14-133-3 revision}

@@

I uploaded a revised version of our manuscript
``\textbf{partykit}: A Modular Toolkit for Recursive Partytioning in R'' to the
Machine Learning Open-Source Software track of the Journal of Machine
Learning Research.

Reviewer~3 suggested to add forest functionality to the \emph{partykit}
package to increase it breadth.
This suggestion was already brought up in the previous revision by
Reviewer~2 and answered to the satisfaction of the first two reviewers:
While the basic idea for setting up a generic class for ``random forests''
is straightforward, many of the details in the implementation are not
obvious at all and deserve much more attention.  
Of course, we could easily copy the code of the old \texttt{party::cforest}
into the new \emph{partykit} package but this would not increase the
usefulness for the practitioner because \emph{party} is easily available. We
therefore decided not to follow the suggestion by reviewer~3 for the same
reasons as explained in the previous round and, in more detail now, the
rebuttal letter.

We revised the manuscript following the Instructions for Authors closely and
will send the copyright forms upon acceptance.

>>>>

\subject{JMLR-14-133-4 revision}

@@

I uploaded a revised version of the \textbf{partykit} package (version
0.8-4, also the current CRAN version). Following the request by referee 3,
we implemented \textbf{cforest()} in this version. The benefits and
shortcomings of this implementation of random forests, compared to the
implementations in the \textbf{randomForest} and \textbf{party} packages, are
discussed in the rebuttal.

The manuscript was not changed and thus I did not upload a new version.
